\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-10 paper.tex
Update diagrams
Edit System Architecture

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{system_design}
    \caption{System Design.}
    \label{fig:system_design}
\end{figure}

>>>>

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who upload data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{system_design}
    \caption{The system design of a decentralized architecture which consist of a registrar, data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}
